Exploratory Analyses: Adaptation

### 2024-05-27 Manuscript Analysis/adaptation_analysis.Rmd
updated adaptation analysis

@@

adapt_pupil <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 35) +
                  te(time_norm, trial_c, k = 35) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m =1),
                discrete = T,
                family = "scat",
                AR.start = start_event,
                rho = .92,
                data = pupil_df)

@@

### By Trial Contours

vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "Control Accurate"), 
        theta = -45, phi = 55, color = "topo")

vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "Control Inaccurate"), 
        theta = -45, phi = 55, color = "topo")

vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "ALS Accurate"), 
        theta = -45, phi = 55, color = "topo")

vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "ALS Inaccurate"), 
        theta = -45, phi = 55, color = "topo")
```

@@

```
### Curve Differences

>>>>

### Main Model

@@

m2_pupil <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 25) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m = 1),
                discrete = T,
                AR.start = start_event,
                rho = .9341941,
                family = "scat",
                data = pupil_df)

### Adaptation Model

adapt_pupil <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 35) +
                  te(time_norm, trial_c, k = 35) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m =1),
                discrete = T,
                family = "scat",
                AR.start = start_event,
                rho = .9341941,
                data = pupil_df)

@@

#### Model Check

@@

#### Model Comparison

compareML(m2_pupil, adapt_pupil, signif.stars = T, suggest.report = T)

```
#### By Trial Contours

control_acc <- vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "Control Accurate"), 
        theta = -45, phi = 55, color = "topo")

control_inacc <- vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "Control Inaccurate"), 
        theta = -45, phi = 55, color = "topo")

ALS_acc <- vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "ALS Accurate"), 
        theta = -45, phi = 55, color = "topo")

ALS_inacc <- vis.gam(adapt_pupil, view = c("time_norm", "trial_c"), 
        cond = list(condition = "ALS Inaccurate"), 
        theta = -45, phi = 55, color = "topo")
```

### Curve Differences
